---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# **Hard coral cover resilience in the Coral Triangle in a context of global decline**

**This repository contains code associated to the article:**

Wicquart, J. *et al.* (*in prep.*). Hard coral cover resilience in the Coral Triangle in a context of global decline.


## 1. Abstract


[To complete]


## 2. How to download this project?

On the project main page on GitHub, click on the green button `Code` and then click on `Download ZIP`


## 3. Datasets used

  * 2020 GCRMN modeled hard coral cover trends
  * Natural Earth Data
  * Coral Reef Watch

## 4. Code description

  * `00_site-coordinates.R`
  * `01_extract_dhw-percent.R`
  * `02_figure-1.R`
  * `03_figure-2.R`
  * `04_figure-3.R`
  * `05_figure-4.R`
  * `06_supp-figure-1.R`
  * `07_supp-figure-2.R`

  * :file_folder: **functions**

    - `data_cleaning.R` 
    - `data_cleaning.R`
    - `data_cleaning.R` Graphical parameters
    - 
    - 
    - 


## 5. How to report issues?

Please report any bugs or issues [HERE](https://github.com/JWicquart/monitoring_workflow/issues).


## 6. Reproducibility parameters

```{r echo=FALSE, message=FALSE}

# 1. Packages used in most R scripts ----

library(tidyverse)
library(magrittr)
library(sf)
library(terra)
library(future)
library(furrr) 
library(patchwork)
library(ggtext)
library(tidytext)

# 2. Print session info ----

sessionInfo()

```
